Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)

### 2022-06-27 Manual.Rmd
truly fixed the html and md issues for manual

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)"
output: github_document
---

>>>>

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for logistic regression (exponential distribution)"
output: 
  html_document:
      keep_md: yes
---
